The Folly of Passwords

### 2014-12-11 paper.tex
Made a fair start on chapter 3 and configured Vagrant to start an OTP network.

>>>>

The chosen OTP system was the OATH Toolkit and specifically its
module for the Unix Pluggable Authentication Module (PAM) system
\parencite{samar1996unified}.

The OATH PAM module is simple to configure on a Debian GNU/Linux desktop
computer and provides one-time password login using any OTP token or mobile
app, such as Google Authenticator.
